Printer ballistics through analysis of character's texture

### 2013-11-17 Printer_Balistics.tex
Editing...

%%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Printer ballistics through gray-level co-occurrence matrix of characters}
\author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel\_rodrigues@aol.com}}\\
Mário Brito\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{britomar@aedu.com}}\\
Maurício Perez\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{mauriciolp84@gmail.com}}\\
Anderson Rocha\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
}

%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\begin{abstract}
Here goes the abstract. 
\end{abstract}

>>>>

%%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Printer ballistics through analysis of character's texture}
\author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel\_rodrigues@aol.com}}\\
Mário Brito\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{britomar@aedu.com}}\\
Maurício Perez\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
\tt\small{mauriciolp84@gmail.com}}\\
Anderson Rocha\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
}

%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\begin{abstract}
We describe a technique for ballistics of printed documents, that is, link a printed document to a especific printer. The principle of this technique is the analysis of character's texture, extracting some properties from the characters of printed and scanned documents, and relate this properties through a co-occurence matrix. This matrix can be used to create a "fingerprint" of characters (and related printers), that allows identify a specific printer device that print these characters.
\end{abstract}
